### 2015-05-14 corral.tex
fixes

We have implemented two different levels of context-switch instrumentation granularity.
%
\textbf{\yieldcoarse} instruments \texttt{yield} statement in a binary fashion: if \whoop
finds that a pair of entry points cannot race, then it will only instrument
context-switches in synchronization points (i.e.\ locks and unlocks) of this pair; else if \whoop finds
that a pair of entry points can race, then it will instrument context-switches
in all visible operations of this pair.
%
\textbf{\yieldmr} is a finer-grained instrumentation: \whoop instruments context-switches
in all synchronization points, but only instruments context-switches in memory
regions that can potentially race (regardless if a pair has not been fully
verified as race-free). In our experiments (see \S\ref{evaluation}),
\yieldmr significantly outperforms \yieldcoarse.

>>>>

We have implemented two different levels of context-switch instrumentation granularity: \yieldcoarse and \yieldmr.
%
The first instruments \texttt{yield} statement in a binary fashion: if \whoop
finds that a pair of entry points cannot race, then it will only instrument
context-switches in synchronization points (i.e.\ locks and unlocks) of this pair; else if \whoop finds
that a pair of entry points can race, then it will instrument context-switches
in all visible operations of this pair.
%
\textbf{\yieldmr} is a finer-grained instrumentation: \whoop instruments context-switches
in all synchronization points, but only instruments context-switches in memory
regions that can potentially race (regardless if a pair has not been fully
verified as race-free). In our experiments (see \S\ref{evaluation}),
\yieldmr significantly outperforms \yieldcoarse.

### 2015-05-14 evaluation.tex
fixes

\noindent\textbf{Granularity of Context-Switches }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times, in seconds, are averages over three runs. \corral was configured with a time budget of 10 hours (T.O. denotes timeout) and a csb of 2, 5 and 9, respectively. For standalone \corral we enable the \yieldall instrumentation, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations. \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see \S\ref{corral}). The table also shows the number of context-switches per instrumentation (\#Y).

>>>>

\noindent\textbf{Accelerating \corral }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times are in seconds and averages over three runs. \corral was configured with a time budget of 10 hours (T.O. denotes timeout) and a csb of 2, 5 and 9, respectively. Standalone \corral uses \yieldall, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations, while \whoop + \corral uses \yieldcoarse and \yieldmr, which instrument context-switches in a more fine-grained fashion (see \S\ref{corral}). The table also shows the number of context-switches per instrumentation (\#Y).
